Concurrent Programming with CXL

### 2020-06-15 book/paper.tex
Latest

You may find the free ``The Little Book of Semaphores'' by
Allen Downey a great resource for working with semaphores.
You can find it at
\underline{http://greenteapress.com/semaphores/LittleBookOfSemaphores.pdf}.

>>>>

You may find the free ``The Little Book of Semaphores'' by
Allen Downey a great resource for working with semaphores~\cite{Downey09}.
